\chapter*{ABSTRACT}
%................................
%................................
This document is a ejemplo prepared to illustrate the use of the \AmS-\LaTeX{} pacakage version~2.2 and the \LaTeX{} \,\verb+puctesis+\, documentclass.

Authors should use the coding in the file \,\verb+puctesis_ejemplo.tex+\, as a model.  This file was used to prepare this ejemplo.

The template file \,\verb+puctesis_plantilla.tex+\, should be of help in getting started with the writing of a new thesis. A verbatim listing of the template file is provided in Appendix~\ref{ap:puctesis} of this document.

The style file, \,\verb+puctesis.sty,+\, and the document class \,\verb+puctesis.cls,+\, are based on style files\hfill from\hfill the\hfill {\sl American\hfill Mathematical\hfill Society\/}\hfill (AMS).\hfill  New\hfill documents\hfill should\hfill employ\hfill the\\
\,\verb+puctesis.cls,+\, document class and be compiled using \LaTeX{} $2_\varepsilon$.  The current version of the \,\verb+puctesis.sty,+\, style file should not be used as it does not comply with the guidelines for thesis preparation.  It is provided only as a reference and to support compilation in the unlikely situation that \LaTeX{} $2_\varepsilon$ is not available and only plain \LaTeX{} is.  Most of the text in this ejemplo document is the same as that usually provided by the AMS with their article and monograph style packages.


           %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
           %   KEYWORDS                                       %
           %--------------------------------------------------%
           %      at the end of the abstract page             %
           %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

~\vfill
{\bf Keywords:} \parbox[t]{.8\textwidth}{thesis template,
  document writing, differential equations, aerodynamics,
  electromagnetic waves theory, shock analysis, elasticity,
  computer simulation, quantum mechanics, 
  \mbox{Campbell-Baker-Hausdorff} formula.
}